---
title: "Human contamination filtering QC"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
execute:
  warning: false
  message: false
params:
  qc_input: "../data/human_contamination_qc.tsv"
  haplogroup_overlap_input: "../data/human_haplogroup_site_overlap.tsv"
  output_status_table: "reports/human_contamination_status.tsv"
---

```{r setup}
qc_root <- if (basename(getwd()) == "analysis") normalizePath("..") else normalizePath(".")
source(file.path(qc_root, "R", "contamination_qc.R"))

resolve_from_qc_root <- function(path) {
  if (grepl("^/", path)) {
    return(path)
  }
  file.path(qc_root, path)
}

qc_input <- resolve_from_qc_root(params$qc_input)
haplogroup_overlap_input <- resolve_from_qc_root(params$haplogroup_overlap_input)
output_status_table <- resolve_from_qc_root(params$output_status_table)

qc_table <- read_optional_table(qc_input)
haplogroup_overlap <- read_optional_table(haplogroup_overlap_input)
qc_table <- classify_contamination(qc_table)
status_summary <- summarize_status(qc_table)
```

## 输入文件

This report is intended to be rendered from the repository-local QC workspace:

```bash
cd qc_analysis
quarto render analysis/05_human_contamination_filtering.qmd
```

Expected inputs live under the repository-level `data/` directory and are referenced from `qc_analysis/` by default:

| Input | Default path | Purpose |
|---|---|---|
| Human contamination QC table | `r params$qc_input` | Per-sample low-VAF and contamination metrics. |
| Human haplogroup site overlap table | `r params$haplogroup_overlap_input` | Sites overlapping known human haplogroup markers. |

```{r input-status}
data.frame(
  input = c("qc_input", "haplogroup_overlap_input"),
  path = c(qc_input, haplogroup_overlap_input),
  exists = c(file.exists(qc_input), file.exists(haplogroup_overlap_input))
)
```

## low-VAF 定义

Low-VAF variants are defined here as candidate heteroplasmic or contaminant-supporting alleles with variant allele fraction between 1% and 5% by default. The helper function `normalize_low_vaf()` in `R/contamination_qc.R` applies this definition and can be reused in upstream table-generation scripts.

## human haplogroup site overlap

Variants that overlap known human haplogroup-informative sites are summarized in this section. These overlaps help distinguish expected primate mitochondrial signal from likely human contamination.

```{r haplogroup-overlap-preview}
if (nrow(haplogroup_overlap) == 0) {
  data.frame(note = "No haplogroup overlap input was found; add the table under data/ to populate this section.")
} else {
  utils::head(haplogroup_overlap, 20)
}
```

## 阈值选择

The default contamination status thresholds are:

- `pass`: contamination score < 0.05
- `review`: contamination score >= 0.05 and < 0.10
- `contaminated`: contamination score >= 0.10
- `not_evaluated`: contamination score missing or unavailable

These thresholds are centralized in `classify_contamination()` so future reports and scripts can share the same classification logic.

## 最终 contamination status

```{r final-status-summary}
if (nrow(status_summary) == 0) {
  data.frame(note = "No QC table was found; add the table under data/ to compute contamination status.")
} else {
  status_summary
}
```

## 图

```{r status-plot, fig.width=7, fig.height=5}
plot_status_counts(status_summary)
```

## 输出表格

The final contamination status table is written to `r params$output_status_table` when QC input rows are available.

```{r write-output-table}
if (nrow(qc_table) > 0) {
  dir.create(dirname(output_status_table), recursive = TRUE, showWarnings = FALSE)
  utils::write.table(qc_table, output_status_table, sep = "\t", quote = FALSE, row.names = FALSE)
  data.frame(output = output_status_table, rows = nrow(qc_table))
} else {
  data.frame(note = "No output table written because the QC input table is unavailable or empty.")
}
```
