---
title: "Reference discovery and materialization status report"
subtitle: "Primate mtDNA preprocessing first-pass diagnostics"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
library(stringr)

fs_available <- requireNamespace("fs", quietly = TRUE)

repo_root <- tryCatch(
  system2("git", c("rev-parse", "--show-toplevel"), stdout = TRUE, stderr = FALSE),
  error = function(e) getwd()
)
repo_root <- normalizePath(repo_root[1], mustWork = TRUE)
knitr::opts_knit$set(root.dir = repo_root)

primary_inputs <- c(
  discovery_summary = "data/metadata/species_reference_chrM_summary.tsv",
  materialization_results = "results/preprocessing/reference_materialization/reference_materialization_manifest.tsv",
  materialization_references = "references/manifests/reference_materialization_manifest.tsv",
  in_house_inputs = "references/manifests/in_house_score_reference_inputs.tsv"
)

file_exists_nonempty <- function(path) {
  file.exists(path) && !is.na(file.info(path)$size) && file.info(path)$size > 0
}

read_tsv_if_exists <- function(path) {
  if (!file_exists_nonempty(path)) {
    return(tibble())
  }
  readr::read_tsv(path, show_col_types = FALSE, col_types = readr::cols(.default = readr::col_character()))
}

has_col <- function(df, col) {
  !is.null(df) && col %in% names(df)
}

first_existing_col <- function(df, candidates) {
  found <- candidates[candidates %in% names(df)]
  if (length(found) == 0) NA_character_ else found[[1]]
}

normalize_missing_values <- function(x) {
  x <- as.character(x)
  x <- str_trim(replace_na(x, ""))
  if_else(x %in% c("", "NA", "N/A", "na", "n/a", ".", "NULL", "null", "None", "none"), NA_character_, x)
}

path_exists <- function(path) {
  path <- normalize_missing_values(path)
  if (is.na(path)) return(FALSE)
  file.exists(path)
}

path_is_dir <- function(path) {
  path <- normalize_missing_values(path)
  if (is.na(path) || !file.exists(path)) return(FALSE)
  if (fs_available) fs::is_dir(path) else isTRUE(file.info(path)$isdir)
}

path_file_size <- function(path) {
  path <- normalize_missing_values(path)
  if (is.na(path) || !file.exists(path) || path_is_dir(path)) return(NA_real_)
  as.numeric(file.info(path)$size)
}

is_fasta_like <- function(path) {
  path <- normalize_missing_values(path)
  if (is.na(path)) return(FALSE)
  str_detect(str_to_lower(path), "\\.(fa|fasta|fna|fa\\.gz|fasta\\.gz|fna\\.gz)$")
}

count_or_message <- function(df, col, label = col) {
  if (is.na(col) || !has_col(df, col)) {
    cat("No `", label, "` column was available; skipping this summary.\n\n", sep = "")
    return(invisible(NULL))
  }
  df %>%
    mutate(value = normalize_missing_values(.data[[col]]), value = replace_na(value, "missing")) %>%
    count(value, sort = TRUE, name = "n") %>%
    knitr::kable(col.names = c(label, "n"))
}

source_col_candidates <- c("reference_source", "ref_source", "source", "wg_source", "chrM_source", "status", "reference_status", "discovery_status")
family_col_candidates <- c("family", "Family", "taxonomic_family")
genus_col_candidates <- c("genus", "Genus")
species_col_candidates <- c("target_species", "species", "Species", "scientific_name", "binomial")
wg_path_candidates <- c("wg_fasta_path", "whole_genome_fasta", "wg_fasta", "whole_fasta", "wg_reference_path", "wg_path", "fasta_path", "local_wg_fasta")
chrm_path_candidates <- c("chrM_fasta_path", "chrm_fasta_path", "chrM_fasta", "chrm_fasta", "mitochondrial_fasta", "mt_fasta", "chrM_reference_path", "chrM_path", "local_chrM_fasta")
embedded_col_candidates <- c("embedded_chrM", "has_embedded_chrM", "embedded_chrM_status", "chrM_embedded", "wg_has_chrM", "contains_chrM")
chrm_acc_candidates <- c("chrM_accession", "chrm_accession", "mitochondrial_accession", "mt_accession")
wg_acc_candidates <- c("wg_accession", "whole_genome_accession", "assembly_accession", "genome_accession")
status_col_candidates <- c("build_status", "status", "materialization_status", "result", "state")
message_col_candidates <- c("build_message", "message", "error", "error_message", "stderr", "reason")
materialized_wg_candidates <- c("materialized_wg_fasta", "wg_fasta_path", "wg_fasta", "whole_fasta", "output_wg_fasta", "local_wg_fasta")
materialized_chrm_candidates <- c("materialized_chrM_fasta", "chrM_fasta_path", "chrM_fasta", "chrm_fasta_path", "chrm_fasta", "output_chrM_fasta", "local_chrM_fasta")

inputs_status <- tibble(
  input_name = names(primary_inputs),
  path = unname(primary_inputs),
  found = file.exists(path),
  nonempty = map_lgl(path, file_exists_nonempty),
  rows = map_int(path, ~ nrow(read_tsv_if_exists(.x)))
)

missing_inputs <- inputs_status %>% filter(!nonempty)

discovery <- read_tsv_if_exists(primary_inputs[["discovery_summary"]])
materialization_results <- read_tsv_if_exists(primary_inputs[["materialization_results"]])
materialization_references <- read_tsv_if_exists(primary_inputs[["materialization_references"]])
in_house_inputs <- read_tsv_if_exists(primary_inputs[["in_house_inputs"]])

species_col <- first_existing_col(discovery, species_col_candidates)
wg_path_col <- first_existing_col(discovery, wg_path_candidates)
chrm_path_col <- first_existing_col(discovery, chrm_path_candidates)
family_col <- first_existing_col(discovery, family_col_candidates)
genus_col <- first_existing_col(discovery, genus_col_candidates)
embedded_col <- first_existing_col(discovery, embedded_col_candidates)
chrm_acc_col <- first_existing_col(discovery, chrm_acc_candidates)
wg_acc_col <- first_existing_col(discovery, wg_acc_candidates)

if (!is.na(species_col) && nrow(discovery) > 0) {
  discovery <- discovery %>% mutate(target_species_report = normalize_missing_values(.data[[species_col]]))
} else {
  discovery$target_species_report <- rep(NA_character_, nrow(discovery))
}

if (!is.na(wg_path_col) && nrow(discovery) > 0) {
  discovery <- discovery %>% mutate(wg_path_report = normalize_missing_values(.data[[wg_path_col]]))
} else {
  discovery$wg_path_report <- rep(NA_character_, nrow(discovery))
}

if (!is.na(chrm_path_col) && nrow(discovery) > 0) {
  discovery <- discovery %>% mutate(chrM_path_report = normalize_missing_values(.data[[chrm_path_col]]))
} else {
  discovery$chrM_path_report <- rep(NA_character_, nrow(discovery))
}

if (is.na(genus_col) && nrow(discovery) > 0) {
  discovery <- discovery %>% mutate(genus_report = str_extract(target_species_report, "^[^_ ]+"))
  genus_col_report <- "genus_report"
} else {
  genus_col_report <- genus_col
}

path_problem_rows <- function(df, path_col, path_label) {
  if (is.na(path_col) || nrow(df) == 0) return(tibble())
  df %>%
    transmute(
      target_species = target_species_report,
      path_type = path_label,
      path_value = .data[[path_col]],
      normalized_path = normalize_missing_values(.data[[path_col]]),
      is_missing_value = is.na(normalized_path),
      exists = map_lgl(normalized_path, path_exists),
      is_directory = map_lgl(normalized_path, path_is_dir),
      fasta_like_extension = map_lgl(normalized_path, is_fasta_like)
    ) %>%
    filter(is_missing_value | is_directory | (exists & !fasta_like_extension))
}

missing_wg <- discovery %>% filter(is.na(wg_path_report))
missing_chrm <- discovery %>% filter(is.na(chrM_path_report))
missing_both <- discovery %>% filter(is.na(wg_path_report), is.na(chrM_path_report))
duplicated_species <- discovery %>%
  filter(!is.na(target_species_report)) %>%
  add_count(target_species_report, name = "target_species_n") %>%
  filter(target_species_n > 1) %>%
  arrange(target_species_report)
duplicated_species_paths <- discovery %>%
  filter(!is.na(target_species_report)) %>%
  add_count(target_species_report, wg_path_report, chrM_path_report, name = "species_path_n") %>%
  filter(species_path_n > 1) %>%
  arrange(target_species_report, wg_path_report, chrM_path_report)
suspicious_paths <- bind_rows(
  path_problem_rows(discovery, wg_path_col, "WG"),
  path_problem_rows(discovery, chrm_path_col, "chrM")
)

materialization_all <- bind_rows(
  materialization_results %>% mutate(manifest_source = primary_inputs[["materialization_results"]]),
  materialization_references %>% mutate(manifest_source = primary_inputs[["materialization_references"]])
)
mat_status_col <- first_existing_col(materialization_all, status_col_candidates)
mat_message_col <- first_existing_col(materialization_all, message_col_candidates)
mat_wg_col <- first_existing_col(materialization_all, materialized_wg_candidates)
mat_chrm_col <- first_existing_col(materialization_all, materialized_chrm_candidates)

if (nrow(materialization_all) > 0) {
  materialization_all <- materialization_all %>%
    mutate(
      mat_status_report = if (!is.na(mat_status_col)) normalize_missing_values(.data[[mat_status_col]]) else NA_character_,
      mat_message_report = if (!is.na(mat_message_col)) normalize_missing_values(.data[[mat_message_col]]) else NA_character_,
      mat_wg_path_report = if (!is.na(mat_wg_col)) normalize_missing_values(.data[[mat_wg_col]]) else NA_character_,
      mat_chrM_path_report = if (!is.na(mat_chrm_col)) normalize_missing_values(.data[[mat_chrm_col]]) else NA_character_,
      mat_failure_category = case_when(
        !is.na(mat_status_report) & str_detect(str_to_lower(mat_status_report), "success|complete|ok|done") ~ "success",
        str_detect(replace_na(mat_message_report, ""), fixed("SIGKILL", ignore_case = TRUE)) ~ "SIGKILL",
        str_detect(replace_na(mat_message_report, ""), fixed("Is a directory", ignore_case = TRUE)) ~ "path_is_directory",
        str_detect(replace_na(mat_message_report, ""), regex("missing.*wg|wg.*missing", ignore_case = TRUE)) ~ "missing_wg",
        str_detect(replace_na(mat_message_report, ""), regex("missing.*chrM|chrM.*missing|missing.*chrm|chrm.*missing", ignore_case = TRUE)) ~ "missing_chrM",
        !is.na(mat_message_report) & mat_message_report != "" ~ "other_message",
        TRUE ~ "unknown_or_not_reported"
      ),
      mat_wg_exists = map_lgl(mat_wg_path_report, path_exists),
      mat_chrM_exists = map_lgl(mat_chrM_path_report, path_exists),
      mat_wg_missing_output = !is.na(mat_wg_path_report) & !mat_wg_exists,
      mat_chrM_missing_output = !is.na(mat_chrM_path_report) & !mat_chrM_exists
    )
}

in_house_species_col <- first_existing_col(in_house_inputs, species_col_candidates)
in_house_wg_col <- first_existing_col(in_house_inputs, c("wg_fasta_path", wg_path_candidates))
in_house_chrm_col <- first_existing_col(in_house_inputs, c("chrM_fasta_path", "chrm_fasta_path", chrm_path_candidates))

if (nrow(in_house_inputs) > 0) {
  in_house_inputs <- in_house_inputs %>%
    mutate(
      ih_target_species = if (!is.na(in_house_species_col)) normalize_missing_values(.data[[in_house_species_col]]) else NA_character_,
      ih_wg_path = if (!is.na(in_house_wg_col)) normalize_missing_values(.data[[in_house_wg_col]]) else NA_character_,
      ih_chrM_path = if (!is.na(in_house_chrm_col)) normalize_missing_values(.data[[in_house_chrm_col]]) else NA_character_,
      ih_wg_exists = map_lgl(ih_wg_path, path_exists),
      ih_chrM_exists = map_lgl(ih_chrM_path, path_exists),
      ih_usable = !is.na(ih_wg_path) & !is.na(ih_chrM_path) & !map_lgl(ih_wg_path, path_is_dir) & !map_lgl(ih_chrM_path, path_is_dir)
    )
}
```

# Overview

```{r overview}
cat("Report generated at:", format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z"), "\n\n")

knitr::kable(inputs_status)

overview_counts <- tibble(
  metric = c(
    "unique_target_species",
    "species_with_usable_wg_reference_path",
    "species_with_usable_chrM_reference_path",
    "species_with_both_wg_and_chrM_paths"
  ),
  value = c(
    n_distinct(discovery$target_species_report, na.rm = TRUE),
    n_distinct(discovery$target_species_report[!is.na(discovery$wg_path_report)], na.rm = TRUE),
    n_distinct(discovery$target_species_report[!is.na(discovery$chrM_path_report)], na.rm = TRUE),
    n_distinct(discovery$target_species_report[!is.na(discovery$wg_path_report) & !is.na(discovery$chrM_path_report)], na.rm = TRUE)
  )
)
knitr::kable(overview_counts)
```

```{r missing-input-warning, results='asis'}
if (nrow(missing_inputs) > 0) {
  cat("::: {.callout-warning}\n")
  cat("## Missing or empty optional input files\n\n")
  cat("The report will continue with available inputs, but these files were missing or empty:\n\n")
  for (p in missing_inputs$path) cat("- `", p, "`\n", sep = "")
  cat(":::\n")
}
```

# Reference discovery summary

```{r discovery-summary}
if (nrow(discovery) == 0) {
  cat("No non-empty discovery summary was available at `", primary_inputs[["discovery_summary"]], "`.\n", sep = "")
} else {
  cat("Discovery rows loaded:", nrow(discovery), "\n\n")
}
```

## Family distribution

```{r family-summary}
count_or_message(discovery, family_col, "family")
```

## Genus distribution

```{r genus-summary}
if (!is.na(genus_col_report)) {
  count_or_message(discovery, genus_col_report, "genus")
} else {
  cat("No genus column was available and genus could not be parsed from species names.\n\n")
}
```

## Reference source/status columns

```{r reference-source-status-summary}
source_status_cols <- intersect(source_col_candidates, names(discovery))
if (length(source_status_cols) == 0) {
  cat("No reference source/status columns were available; skipping this summary.\n\n")
} else {
  for (col in source_status_cols) {
    cat("### `", col, "`\n\n", sep = "")
    print(count_or_message(discovery, col, col))
    cat("\n\n")
  }
}
```

## Embedded chrM status

```{r embedded-chrm-summary}
count_or_message(discovery, embedded_col, "embedded chrM status")
```

## chrM accession availability

```{r chrm-accession-summary}
if (!is.na(chrm_acc_col)) {
  discovery %>%
    mutate(chrM_accession_available = !is.na(normalize_missing_values(.data[[chrm_acc_col]]))) %>%
    count(chrM_accession_available, name = "n") %>%
    knitr::kable()
} else {
  cat("No chrM accession column was available; skipping this summary.\n\n")
}
```

## WG accession availability

```{r wg-accession-summary}
if (!is.na(wg_acc_col)) {
  discovery %>%
    mutate(wg_accession_available = !is.na(normalize_missing_values(.data[[wg_acc_col]]))) %>%
    count(wg_accession_available, name = "n") %>%
    knitr::kable()
} else {
  cat("No WG accession column was available; skipping this summary.\n\n")
}
```

# Missing reference diagnostics

## Missing WG paths

```{r missing-wg}
DT::datatable(missing_wg, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

## Missing chrM paths

```{r missing-chrm}
DT::datatable(missing_chrm, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

## Missing both WG and chrM paths

```{r missing-both}
DT::datatable(missing_both, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

## Duplicated target species

```{r duplicated-target-species}
DT::datatable(duplicated_species, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

## Duplicated species/reference path combinations

```{r duplicated-species-paths}
DT::datatable(duplicated_species_paths, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

## Suspicious paths

```{r suspicious-paths}
DT::datatable(suspicious_paths, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

# Reference materialization summary

```{r materialization-summary}
if (nrow(materialization_all) == 0) {
  cat("No non-empty reference materialization manifest was available.\n\n")
} else {
  cat("Materialization rows loaded:", nrow(materialization_all), "\n\n")

  if (!is.na(mat_status_col)) {
    materialization_all %>% count(manifest_source, mat_status_report, sort = TRUE, name = "n") %>% knitr::kable()
  } else {
    cat("No materialization status/build_status column was available.\n\n")
  }

  if (!is.na(mat_message_col)) {
    materialization_all %>% count(mat_failure_category, sort = TRUE, name = "n") %>% knitr::kable()
  } else {
    cat("No materialization build_message/message/error column was available.\n\n")
  }

  mat_output_counts <- tibble(
    metric = c("materialized_WG_FASTA_files", "materialized_chrM_FASTA_files", "missing_output_FASTA_files"),
    value = c(
      sum(materialization_all$mat_wg_exists),
      sum(materialization_all$mat_chrM_exists),
      sum(materialization_all$mat_wg_missing_output | materialization_all$mat_chrM_missing_output)
    )
  )
  knitr::kable(mat_output_counts)
}
```

## Failed or problematic materialization rows

```{r materialization-problem-table}
materialization_problem_rows <- if (nrow(materialization_all) == 0) {
  tibble()
} else {
  materialization_all %>%
    filter(
      is.na(mat_status_report) |
        !str_detect(str_to_lower(mat_status_report), "success|complete|ok|done") |
        mat_wg_missing_output |
        mat_chrM_missing_output
    )
}
DT::datatable(materialization_problem_rows, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

# In-house score input readiness

```{r in-house-readiness}
if (nrow(in_house_inputs) == 0) {
  cat("No non-empty in-house score input manifest was available at `", primary_inputs[["in_house_inputs"]], "`.\n", sep = "")
  in_house_summary <- tibble(metric = character(), value = integer())
  in_house_duplicates_species <- tibble()
  in_house_duplicates_paths <- tibble()
  in_house_not_usable <- tibble()
} else {
  in_house_duplicates_species <- in_house_inputs %>%
    filter(!is.na(ih_target_species)) %>%
    add_count(ih_target_species, name = "target_species_n") %>%
    filter(target_species_n > 1)

  in_house_duplicates_paths <- in_house_inputs %>%
    filter(!is.na(ih_target_species)) %>%
    add_count(ih_target_species, ih_wg_path, ih_chrM_path, name = "species_path_n") %>%
    filter(species_path_n > 1)

  in_house_not_usable <- in_house_inputs %>% filter(!ih_usable)

  in_house_summary <- tibble(
    metric = c(
      "total_input_rows",
      "unique_target_species",
      "rows_with_wg_fasta_path_present",
      "rows_with_chrM_fasta_path_present",
      "rows_with_both_paths_present",
      "duplicated_target_species_rows",
      "duplicated_target_species_wg_chrM_path_rows"
    ),
    value = c(
      nrow(in_house_inputs),
      n_distinct(in_house_inputs$ih_target_species, na.rm = TRUE),
      sum(!is.na(in_house_inputs$ih_wg_path)),
      sum(!is.na(in_house_inputs$ih_chrM_path)),
      sum(!is.na(in_house_inputs$ih_wg_path) & !is.na(in_house_inputs$ih_chrM_path)),
      nrow(in_house_duplicates_species),
      nrow(in_house_duplicates_paths)
    )
  )
  knitr::kable(in_house_summary)
}
```

## Rows not usable for in-house scoring

```{r in-house-not-usable-table}
DT::datatable(in_house_not_usable, filter = "top", options = list(pageLength = 25, scrollX = TRUE), rownames = FALSE)
```

# Plots

## Reference/materialization status

```{r materialization-status-plot, fig.width=9, fig.height=5}
if (nrow(materialization_all) > 0 && !is.na(mat_status_col)) {
  ggplot(materialization_all, aes(x = mat_status_report, fill = manifest_source)) +
    geom_bar(position = "dodge") +
    labs(x = "Materialization status", y = "Rows", fill = "Manifest source") +
    theme_minimal(base_size = 12) +
    theme(axis.text.x = element_text(angle = 35, hjust = 1))
} else {
  cat("No materialization status column was available for plotting.\n")
}
```

## Family or genus counts

```{r family-genus-plot, fig.width=9, fig.height=5}
plot_group_col <- if (!is.na(family_col)) family_col else genus_col_report
plot_group_label <- if (!is.na(family_col)) "family" else "genus"
if (!is.na(plot_group_col) && nrow(discovery) > 0) {
  plot_data <- discovery %>%
    mutate(group = replace_na(normalize_missing_values(.data[[plot_group_col]]), "missing")) %>%
    count(group, sort = TRUE) %>%
    slice_head(n = 25)
  ggplot(plot_data, aes(x = reorder(group, n), y = n)) +
    geom_col() +
    coord_flip() +
    labs(x = plot_group_label, y = "Species/row count") +
    theme_minimal(base_size = 12)
} else {
  cat("No family or genus information was available for plotting.\n")
}
```

## WG/chrM availability

```{r wg-chrm-availability-plot, fig.width=8, fig.height=5}
availability_plot_data <- discovery %>%
  transmute(
    availability = case_when(
      !is.na(wg_path_report) & !is.na(chrM_path_report) ~ "both WG and chrM",
      !is.na(wg_path_report) & is.na(chrM_path_report) ~ "WG only",
      is.na(wg_path_report) & !is.na(chrM_path_report) ~ "chrM only",
      TRUE ~ "missing both"
    )
  ) %>%
  count(availability, name = "n")

ggplot(availability_plot_data, aes(x = availability, y = n, fill = availability)) +
  geom_col(show.legend = FALSE) +
  labs(x = "Reference path availability", y = "Rows") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```

# Suggested next actions

```{r suggested-next-actions, results='asis'}
issues <- 0L

if (nrow(missing_wg) > 0 || nrow(missing_chrm) > 0) {
  issues <- issues + 1L
  cat("::: {.callout-warning}\n")
  cat("## Missing reference paths\n\n")
  cat("- Missing WG paths: ", nrow(missing_wg), " rows. Inspect the `Missing WG paths` table above.\n", sep = "")
  cat("- Missing chrM paths: ", nrow(missing_chrm), " rows. Inspect the `Missing chrM paths` table above.\n", sep = "")
  cat(":::\n\n")
}

if (nrow(duplicated_species) > 0) {
  issues <- issues + 1L
  cat("::: {.callout-warning}\n")
  cat("## Duplicated target species\n\n")
  cat("There are ", nrow(duplicated_species), " rows involved in duplicated `target_species` values. Downstream score/reference build steps may use unexpected duplicate rows.\n", sep = "")
  cat(":::\n\n")
}

if (nrow(in_house_inputs) > 0 && nrow(discovery) > 0) {
  discovery_unique <- n_distinct(discovery$target_species_report, na.rm = TRUE)
  in_house_unique <- n_distinct(in_house_inputs$ih_target_species, na.rm = TRUE)
  if (in_house_unique < discovery_unique) {
    issues <- issues + 1L
    cat("::: {.callout-warning}\n")
    cat("## Fewer species in in-house score inputs\n\n")
    cat("`in_house_score_reference_inputs.tsv` has ", in_house_unique,
        " unique species, compared with ", discovery_unique,
        " unique species in `species_reference_chrM_summary.tsv`.\n", sep = "")
    cat(":::\n\n")
  }
}

if (issues == 0L && nrow(missing_inputs) == 0 && nrow(in_house_not_usable) == 0) {
  cat("::: {.callout-tip}\n")
  cat("## Ready for in-house score\n\n")
  cat("All required inputs that were checked look complete for reference discovery/materialization and in-house score readiness.\n")
  cat(":::\n")
} else if (issues == 0L) {
  cat("No blocking discovery/materialization issues were detected from the available inputs, but review missing optional inputs and unusable in-house rows above if present.\n")
}
```

# Session info

```{r session-info}
sessionInfo()
```
